When does vapor pressure deficit drive or reduce evapotranspiration?

### 2018-05-25 doc/paper/body.tex
figs, data and citations now match data policy, just need to proofread body and then can submit v2 to arxiv

\section{Materials and Methods}
\subsection{Data}
\label{data}
We use both meteorological and eddy-covariance data from the
FLUXNET2015 database (data available at \sloppy
\url{https://fluxnet.fluxdata.org/data/fluxnet2015-dataset/} \sloppy),
including all sites with at least four years of data and observations
of the variables described in the methods section (Section
\ref{methods}). Seventy-three sites met these requirements, and were
grouped into nine plant functional types (PFT) according to the
International Geosphere-Biosphere Programme vegetation classification
scheme \citep{Loveland_1999}: cropland (CRO), grass (GRA), deciduous
broadleaf forest (DBF), evergreen broadleaf forest (EBF), evergreen
needleleaf forest (ENF), mixed forest (MF), closed shrub (CSH),
savannah (SAV), and woody savannah (WSA) (site locations and citations in Figure
\ref{map_fig} and Table \ref{flux_sites}).

@@

\begin{table}
  \caption{Metadata and citations for flux sites used in this analysis. All data are gathered from \url{www.fluxdata.org} using tools available at \url{https://github.com/trevorkeenan/FLUXNET_citations}.}
  \label{flux_sites}
  \label{definitions}
  \centering \footnotesize
  \begin{tabular}{l l l l l l l}
    \hline
    Site name & PFT & Lat & Lon & Clim$^{a}$ & Period & References \\
    \hline
    \input{flux_sites.tex}
    \hline
    \multicolumn{7}{l}{$^{a}$K{\"o}ppen Climate classification.}
    \hline
\end{table}

@@

>>>>

\section{Materials and Methods}
\subsection{Data}
\label{data}
We use both meteorological and eddy-covariance data from the
FLUXNET2015 database (data available at \sloppy
\url{https://fluxnet.fluxdata.org/data/fluxnet2015-dataset/} \sloppy),
including all sites with at least four years of data and observations
of the variables described in the methods section (Section
\ref{methods}). Seventy-three sites met these requirements, and were
grouped into nine plant functional types (PFT) according to the
International Geosphere-Biosphere Programme vegetation classification
scheme \citep{Loveland_1999}: cropland (CRO), grass (GRA), deciduous
broadleaf forest (DBF), evergreen broadleaf forest (EBF), evergreen
needleleaf forest (ENF), mixed forest (MF), closed shrub (CSH),
savannah (SAV), and woody savannah (WSA) (site locations and citations in Figure
\ref{map_fig} and Appendex \ref{flux_sites}).

@@

@@

\begin{appendices}
  \section{FLUXNET2015 sites}\label{flux_sites}
  % below taken adapted from Trevor Keenan's FLUXNET citations
  % at github.com/trevorkeenan/FLUXNET_citations
  Table A1: Metadata and citations for flux sites used in this analysis. All data are gathered from \url{www.fluxdata.org}, and citations are aggregated using tools available at \url{https://github.com/trevorkeenan/FLUXNET_citations}.
  \begin{longtable}{l l l l l l l}
    \hline 
    \textbf{Site} & 
    \textbf{PFT} & 
    \textbf{Lat} & 
    \textbf{Lon} & 
    \textbf{Clim\textsuperscript{1}} & 
    \textbf{Period} & 
    \textbf{References} \\
    [0.5ex] 
    \hline 
    \input{flux_sites.tex}
    [1ex]
    \hline
  \end{longtable}

  \textsuperscript{1}  K{\"o}ppen Climate classification.
\end{appendices}
